Getting start

### 2023-05-09 inst/gitbook/01_getting_started.Rmd
updated time warning for low spec rate

## Setting the stopping rule (stop when reaching a total of 50 taxa)
stop_rule <- list(max.taxa = 50)

@@

Interestingly, with all our parameters used here and our specific disparity metric we cannot detect the effect of a mass extinction.

>>>>

## Setting the stopping rule (stop after 30 time units)
stop_rule <- list(max.time = 30)

@@

Interestingly, with all our parameters used here and our specific disparity metric we cannot detcet the effect of a mass extinction.
